---
title: "FRBtstrapNotes"
author: "John Saldanha"
date: "2/1/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Documented here various code useful in  constructing 
## the Fill Rate Bootstrap Algorithm and experiments 

We are going to set the working directory as:
# Set the working directory
setwd("/Users/beuser/Documents/Work/Research/Solo Research/Bootstrap Research/
Bootstrap Fill Rate/") 

We read in distribution parameters inputs
```{r}
ExpInputs<-read.csv("ExpInputs.csv")
ExpInputs[1,3] #pick out individual experimental inputs
```


#BELOW ARE ALL THE CODE USED IN THE BOOTSTRAP FR ALGORITHM AND EXPERIMENTS VERBATIM

# Use a fixed random seed to replicate the experiments
set.seed(931971)

# From https://stackoverflow.com/questions/11530010/how-to-simulate-bimodal-distribution
# Function to create a bimodal distribution
mu1 <- 10; mu2 <- 20; sig1 <- 3; sig2 <- 3; pi <- 0.5 
bimodDistFunc <- function (n,pi, mu1, mu2, sig1, sig2) {
  y0 <- rgamma(n,mu1^2/sig1^2, mu1/sig1^2)
  y1 <- rnorm(n,mean=mu2, sd = sig2)
  
  pct <- rbinom(n,size=1,prob=pi)
  y <- y0*(1 - pct) + y1*pct 
}

bimodalData <- bimodDistFunc(n=100,pi,mu1,mu2, sig1,sig2)
hist(bimodalData)

#Lognormal Distributions
ln<-rlnorm(10E6,meanlog=4.585559829,sdlog=0.1980422) 
hist(lognorm)
mean(lognorm)

#Example of sumproduct
x<-c(1,2,3,4) #create a vector x
y<-c(4,3,2,1) #create a vector y
z<-sum(x*y) #sumproduct
A<-matrix(1:9,nrow = 3,ncol = 3,byrow = TRUE) #create 3x3 matrix, values in rows
B<-matrix(9:1,nrow = 3,ncol = 3,byrow = TRUE) #create 3x3 matrix, values in cols
sum(A[,1]*B[,3]) #sumproduct of columns
B[,3] #reference a col

#Pick a random sample of size n_\tilde{X}
tildeX<-rlnorm(24,meanlog=4.585559829,sdlog=0.1980422) #random draw of n_\tilde{X} for LTD data \tilde{X}

BtSmplX<-replicate(5,sort(sample(tildeX,size=24,replace = TRUE))) #Bootstrap sample of tilde X

###### FIXED Q FILL RATE ALGORITHM ######

library(Rfast) #Load library to find nth smallest value in list

#Inputs
P2<-0.98 #Fill rate target
Q<-1000 #Fixed order quantity
nX<-24 #no. of LTD data
#ln the lsit of random 

#lnS<-sort(ln) #sorted LTD data

# Define a function to estimate the expected shorts for every \tilde{X}
ExpShort<-function(x,n)
  {
    short<-1:n
    for (i in 1:n)
      {
        short[i]<-((sum(x[i:n])-x[i]*(n-i+1))/n)*sd(x)
      }
    return(short)
  }

#es<-ExpShort(lnS,nX) #Trying the expected shorts function on an atomic vector

P2lst1<-1-(es/Q) #calculate the P2 for all LTD
P2lst2<-abs(P2-(1-(es/Q))) #calculate the diff of LTD P2 from target fill rate

small2<-nth(P2lst2, 2, descending = F) #2nd smallest diff of LTD P2 from target fill rate
small1<-nth(P2lst2, 1, descending = F) #smallest diff of LTD P2 from target fill rate

small1pos<-match(small1,P2lst2) #position of smallest P2 diff
small2pos<-match(small2,P2lst2) #position of 2nd smallest P2 diff

if (small1pos<small2pos) 
  {
s_hat<-(((P2-P2lst1[small1pos])*(lnS[small2pos]-lnS[small1pos]))/
  (P2lst1[small2pos]-P2lst1[small1pos]))+lnS[small1pos]
  } else 
  {
s_hat<-(((P2-P2lst1[small2pos])*(lnS[small1pos]-lnS[small2pos]))/
  (P2lst1[small1pos]-P2lst1[small2pos]))+lnS[small2pos]
  }

######        END ALGORITHM       ######

#trial<-data.frame(lnS,P2lst1,P2lst2) #This would join all three data sets into one

esMat<-apply(BtSmplX,MARGIN=2,FUN = ExpShort,n=24)


#%%%%%%%%%%%%%%%%%%%%% CALCULATE THE TRUE ROP FROM ANALYTICAL INTEGRATION %%%%%%%%%%%%%%%%%%%%%
# ALSO SEE HERE FOR THE GAMMA ROP ESTIMATE WHEN P2 <= 0.9

# Calculate the True ROP FPR  0.9 < P_2 <= 0.9

# The error function
erf <- function(x) 2 * pnorm(x * sqrt(2)) - 1


# UNIFORM DISTRIBUTION

# Case 1: P2 > 0.9
P2<-0.98
Q<-94
mu<-100
sig<-20
a<-66
b<-134

sU1<-Q*(1-P2)*(b-a)+b

# Case 2: P2 <= 0.9
P2<-0.8
Q<-19
mu<-100
sig<-20
a<-66
b<-134

sU2<-P2*(b-a)+a-(Q/2)

# TRUNCATED NORMAL DISTRIBUTION
library(truncnorm)
#curve(dnorm(x,100,20),from = 0,to=300)

# Case 1: P2 > 0.9

P2<-0.80
Q<-19
mu<-100
sig<-20

#Truncated Normal Expected Shorts
TNES<-function(z)
{
  ((mu-z)*sqrt(pi/2)+sig*exp(-(1/2)*((z-mu)/sig)^2)+
     sig*sqrt(pi/2)*((z-mu)/sig)*erf((z-mu)/(sig*sqrt(2))))/
    (sqrt(2*pi)*(1-0.5*(1+erf(-mu/(sig*sqrt(2))))))
}

sTN1<-optimize(function(z){abs(Q*(1-P2)-(((mu-z)*sqrt(pi/2)+sig*exp(-(1/2)*((z-mu)/sig)^2)+
                                      sig*sqrt(pi/2)*((z-mu)/sig)*erf((z-mu)/(sig*sqrt(2))))/
                                      (sqrt(2*pi)*(1-0.5*(1+erf(-mu/
                                      (sig*sqrt(2))))))))},lower=0,upper=(mu+6*sig))$minimum

#sN1<-optimize(function(z){abs(((Q/sig)*(1-P2))-((dnorm(z)-
#                                z*(1-pnorm(z)))))},lower = 0,upper = 6)$minimum*sig+mu
curve(TNES(x),from = 0,to=mu+6*sig)

# Case 2: P2 <= 0.9

P2<-0.85
Q<-25
mu<-100
sig<-20

TNVQ<-function(z){(1/(2*sqrt(pi)*(1-(1/2)*(1+erf(-mu/(sig*sqrt(2)))))))*
                         (sig*sqrt(2)*(exp(-(Q+z-mu)^2/(2*sig^2))-
                                         exp(-(z-mu)^2/(2*sig^2)))+
                            sqrt(pi)*((mu-z)*erf((z-mu)/(sig*sqrt(2)))+
                                        (Q+z-mu)*erf((Q+z-mu)/(sig*sqrt(2)))+
                                        Q*erf(mu/(sig*sqrt(2)))))}

sTN2<-optimize(function(z){abs(P2-
      ((1/(2*sqrt(pi)*(1-(1/2)*(1+erf(-mu/(sig*sqrt(2)))))))*
      (sig*sqrt(2)*(exp(-(Q+z-mu)^2/(2*sig^2))-exp(-(z-mu)^2/(2*sig^2)))+
      sqrt(pi)*((mu-z)*erf((z-mu)/(sig*sqrt(2)))+
                  (Q+z-mu)*erf((Q+z-mu)/(sig*sqrt(2)))+
                  Q*erf(mu/(sig*sqrt(2))))))/
      Q)},lower=0,upper=(mu+6*sig))$minimum


curve(VQ(x),from = 0,to = 300)

#sN2<-optimize(function(z){abs(((Q/sig)*(1-P2))-((dnorm(z)-z*(1-pnorm(z)))-
#                        (dnorm(z+Q/sig)-(z+Q/sig)*(1-pnorm(z+Q/sig)))))},
#             lower = 0,upper = 6)$minimum*sig+mu

# LOGNORMAL DISTRIBUTION
# The comparison of the lognormal and normal graphs below shows the marginal difference in s
#   for expected shorts calculated by the lognormal and normal distributions below
curve(dlnorm(x,4.585559829,0.1980422),from = 0,to=300)
curve(dnorm(x,100,20),from = 0,to=300)

# Case 1: > 0.9

P2<-0.95
Q<-44
mu<-4.585559829
sig<-0.1980422
CV<-0.2

#Truncated Normal Expected Shorts
LnES<-function(z)
{
  1/2*(exp(mu+sig^2/2)-z-z*erf((mu-log(z))/(sig*sqrt(2)))+
         exp(mu+sig^2/2)*erf((mu+sig^2-log(z))/(sig*sqrt(2))))
}

sLN1<-optimize(function(z){abs(abs(Q*(1-P2))-
                                 (1/2*(exp(mu+sig^2/2)-z-z*erf((mu-log(z))/(sig*sqrt(2)))+
                                 exp(mu+sig^2/2)*erf((mu+sig^2-log(z))/
                                 (sig*sqrt(2))))))},lower=0,upper=(100+6*CV*100))$minimum

curve(LnES(x),from = 0,to=100+6*20)

muX<-100
sigX<-20
sN1<-optimize(function(z){abs(((Q/sigX)*(1-P2))-((dnorm(z)-
                                    z*(1-pnorm(z)))))},lower = 0,upper = 6)$minimum*sigX+muX

# Case 2: P2 <= 0.9
P2<-0.8
Q<-19
mu<-4.585559829
sig<-0.1980422
CV<-0.2



sLN2<-optimize(function(z){abs(P2-
          (Q/2*(1-erf((mu-log(z))/(sig*sqrt(2))))+
          (z+Q)/2*(erf((mu-log(z))/(sig*sqrt(2)))-erf((mu-log(z+Q))/
                                                         (sig*sqrt(2))))-
          exp(mu+sig^2/2)/2*(erf((mu+sig^2-log(z))/(sig*sqrt(2)))-
                               erf((mu+sig^2-log(z+Q))/(sig*sqrt(2)))))/
            Q)},lower=0,upper=(100+6*CV*100))$minimum

muX<-100
sigX<-20
sN1<-optimize(function(z){abs(((Q/sigX)*(1-P2))-((dnorm(z)-z*(1-pnorm(z)))-
                        (dnorm(z+Q/sigX)-(z+Q/sigX)*(1-pnorm(z+Q/sigX)))))},
                        lower = 0,upper = 6)$minimum*sigX+muX

# Bimodal Distribution

# Case 1: P2 > 0.9
P2<-0.95
Q<-44
mu1<-85.9
sig1<-8.6
mu2<-121.1
sig2<-12.1
p<-0.6
q<-0.4 # q = 1-p
CV<-0.2

BMES<-function(z){p*z/2*(erf((z-mu1)/(sig1*sqrt(2)))-1)-mu1*p/2*(erf((z-mu1)/(sig1*sqrt(2)))-1)+
    p/sqrt(2*pi)*sig1*exp(-(z-mu1)^2/(2*sig1^2))+
    q*z/2*(erf((z-mu2)/(sig2*sqrt(2)))-1)-mu2*q/2*(erf((z-mu2)/(sig2*sqrt(2)))-1)+
    q/sqrt(2*pi)*sig2*exp(-(z-mu2)^2/(2*sig2^2))}

curve(BMES(x),from = 0,to=100+6*20)

sBM1<-optimize(function(z)
  {abs(abs(Q*(1-P2))-(p*z/2*(erf((z-mu1)/(sig1*sqrt(2)))-1)-mu1*p/2*(erf((z-mu1)/(sig1*sqrt(2)))-1)+
        p/sqrt(2*pi)*sig1*exp(-(z-mu1)^2/(2*sig1^2))+
        q*z/2*(erf((z-mu2)/(sig2*sqrt(2)))-1)-mu2*q/2*(erf((z-mu2)/(sig2*sqrt(2)))-1)+
        q/sqrt(2*pi)*sig2*exp(-(z-mu2)^2/(2*sig2^2))))},
  lower=0,upper=(100+6*CV*100))$minimum


# Case 2: P2 <= 0.9

P2<-0.8
Q<-19
mu1<-85.9
sig1<-8.6
mu2<-121.1
sig2<-12.1
p<-0.6
q<-0.4 # q = 1-p
CV<-0.2

BMVQ<-function(z)
  {1/sqrt(2*pi)*((z+Q)*sqrt(pi/2)*(p*erf((z+Q-mu1)/(sig1*sqrt(2)))-
   p*erf((z-mu1)/(sig1*sqrt(2)))+(p-1)*(erf((z-mu2)/(sig2*sqrt(2)))-erf((Q+z-mu2)/
   (sig2*sqrt(2)))))+Q*sqrt(pi/2)*(p*erf((z-mu1)/(sig1*sqrt(2)))+p*erf(mu1/(sig1*sqrt(2)))-
   (p-1)*(erf((z-mu2)/(sig2*sqrt(2)))+erf(mu2/(sig2*sqrt(2)))))+mu1*p*sqrt(pi/2)*
   (erf((z-mu1)/(sig1*sqrt(2)))-erf((z+Q-mu1)/(sig1*sqrt(2))))+mu2*(p-1)*sqrt(pi/2)*
   (erf((Q+z-mu2)/(sig2*sqrt(2)))-erf((z-mu2)/(sig2*sqrt(2))))+
   p*sig1*(exp(-(z+Q-mu1)^2/(2*sig1^2))-exp(-(z-mu1)^2/(2*sig1^2)))+
  (sig2-p*sig2)*exp(-(z+Q-mu2)^2/(2*sig2^2))+(p*sig2*-sig2)*exp(-(z-mu2)^2/(2*sig2^2)))}

curve(BMVQ(x),from=0, to=100+6*100*CV)

sBM2<-optimize(function(z)
  {abs(P2-(1/sqrt(2*pi)*((z+Q)*sqrt(pi/2)*(p*erf((z+Q-mu1)/(sig1*sqrt(2)))-
  p*erf((z-mu1)/(sig1*sqrt(2)))+(p-1)*(erf((z-mu2)/(sig2*sqrt(2)))-erf((Q+z-mu2)/
  (sig2*sqrt(2)))))+Q*sqrt(pi/2)*(p*erf((z-mu1)/(sig1*sqrt(2)))+p*erf(mu1/(sig1*sqrt(2)))-
  (p-1)*(erf((z-mu2)/(sig2*sqrt(2)))+erf(mu2/(sig2*sqrt(2)))))+mu1*p*sqrt(pi/2)*
  (erf((z-mu1)/(sig1*sqrt(2)))-erf((z+Q-mu1)/(sig1*sqrt(2))))+mu2*(p-1)*sqrt(pi/2)*
  (erf((Q+z-mu2)/(sig2*sqrt(2)))-erf((z-mu2)/(sig2*sqrt(2))))+
  p*sig1*(exp(-(z+Q-mu1)^2/(2*sig1^2))-exp(-(z-mu1)^2/(2*sig1^2)))+
  (sig2-p*sig2)*exp(-(z+Q-mu2)^2/(2*sig2^2))+(p*sig2*-sig2)*exp(-(z-mu2)^2/(2*sig2^2))))/Q)},
  lower=0,upper=(100+6*CV*100))$minimum

#%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

# Gamma distribution All P2 no double counting To be used in calculating the Silver (1970)
#   modification for P2<= 0.9.

#curve(dlnorm(x,4.585559829,0.1980422),from = 0,to=300)

P2<-0.8
Q<-19
mu<-100
sig<-20
alpha<-mu^2/sig^2
beta<-mu/sig^2
CV<-0.2

EVQGam<-function(z){Q*pgamma(z,alpha,beta)+(z+Q)*
    (pgamma(z+Q,alpha,beta)-pgamma(z,alpha,beta))-(alpha/beta)*(pgamma(z+Q,alpha+1,beta)-
                                                                pgamma(z,alpha+1,beta))}

#curve(EVQGam(x),from = 0,to=mu+6*sig)
#curve(dgamma(x,alpha,beta),from = 0,to=mu+6*sig)
#curve(dnorm(x,mu,sig),from = 0,to=mu+6*sig)

sGam<-optimize(function(z){abs(P2-
                                (Q*pgamma(z,alpha,beta)+(z+Q)*(pgamma(z+Q,alpha,beta)-
                                pgamma(z,alpha,beta))-(alpha/beta)*(pgamma(z+Q,alpha+1,beta)-
                                pgamma(z,alpha+1,beta)))/
                                 Q)},lower=0,upper=(100+6*CV*100))$minimum

#sN2<-optimize(function(z){abs(((Q/sig)*(1-P2))-((dnorm(z)-z*(1-pnorm(z)))-
#                        (dnorm(z+Q/sig)-(z+Q/sig)*(1-pnorm(z+Q/sig)))))},
#              lower = 0,upper = 6)$minimum*sig+mu


